Privacy Policy
Our Privacy Policy was last updated on 25/08/2023. This Privacy Policy describes Our policies and procedures on the collection, use and disclosure of Your information when You use the Application and tells You about Your privacy rights and how the law protects You.
We use Your Personal data to provide and improve the Application. By using the Application, You agree to the collection and use of information in accordance with this Privacy Policy.
Interpretation and Definitions
Interpretation
The words of which the initial letter is capitalized have meanings defined under the following conditions. The following definitions shall have the same meaning regardless of whether they appear in singular or in plural.
Definitions
For the purposes of this Privacy Policy:
● "Account" means a unique account created for You to access our Application or parts of our Application.
● "Application" means the software program provided by the Company downloaded by You on any electronic device, named BeBoom.
● "Company" (referred to as either "the Company", "We", "Us" or "Our" in this Agreement).
● "Country" refers to Brazil.
● "Device" means any device that can access the Application such as a cell phone or a digital tablet.
● "OS" means the Operating System that is accessing the Application (for example, Android 14 SDK 34).
● "Personal Data" is any information that relates to an identified or identifiable individual.
● "Usage Data" refers to data collected automatically, either generated by the use of the Application or from the Application infrastructure itself (for example, the duration You stay in the Application).
● "You" means the individual accessing or using the Application, or the company, or other legal entity on behalf of which such individual is accessing or using the Application, as applicable.
Collecting and Using Your Personal Data
Types of Data Collected
Personal Data
While using Our Application, We may ask You to provide Us with certain personally identifiable information that can be used to contact or identify You. Personally identifiable information may include, but is not limited to:
● Email address 
● Full name 
● Phone number 
● Address, State, Province, ZIP/Postal code, City 
● Date of Birth
● CPF
● Usage Data
Usage Data
Usage Data is collected automatically when using the Application.
Usage Data may include information such as Your Device's Internet Protocol address (e.g. IP address), location, OS  version, the screens of our Application that You visit, the time and date of Your visit, the time spent on those pages, unique device identifiers and other diagnostic data.
We may also collect information that Your device sends whenever You visit our Application or when You access the Application by or through a mobile device
Information Collected while Using the Application
While using Our Application, in order to provide features of Our Application, We may collect, with Your prior permission:
● Information regarding your location
We use this information to provide features of Our Application, to improve and customize Our Application. The information may be uploaded to the Company's servers and/or a service provider's server or it may be simply stored on Your device.
You can enable or disable access to this information at any time, through Your Device’s OS settings.
Use of Your Personal Data
The Company may use Personal Data for the following purposes:
● To provide and maintain our Application, including to monitor the usage of our Application.
● To manage Your Account: to manage Your registration as a user of the Application. The Personal Data You provide can give You access to different functionalities of the Application that are available to You as a registered user.
● To contact You: To contact You by email, telephone calls, SMS, or other equivalent forms of electronic communication, such as a mobile application's push notifications regarding updates or informative communications related to the functionalities, products or contracted services, including the security updates, when necessary or reasonable for their implementation
● To manage Your requests: To attend and manage Your requests to Us.
● For other purposes: We may use Your information for other purposes, such as data analysis, identifying usage trends, determining the effectiveness of our promotional campaigns and to evaluate and improve our Application, products, services, marketing and your experience.
We may share Your personal information in the following situations:
● With other users: when You share personal information or otherwise interact in the public areas with other users, such information may be viewed by all users and may be publicly distributed outside.
● With Your consent: We may disclose Your personal information for any other purpose with Your consent.
Retention of Your Personal Data
The Company will retain Your Personal Data only for as long as is necessary for the purposes set out in this Privacy Policy. We will retain and use Your Personal Data to the extent necessary to comply with our legal obligations (for example, if we are required to retain your data to comply with applicable laws), resolve disputes, and enforce our legal agreements and policies.
The Company will also retain Usage Data for internal analysis purposes. Usage Data is generally retained for a shorter period of time, except when this data is used to strengthen the security or to improve the functionality of Our Application, or We are legally obligated to retain this data for longer time periods.
Transfer of Your Personal Data
Your information, including Personal Data, is processed at the Company's operating offices and in any other places where the parties involved in the processing are located. It means that this information may be transferred to — and maintained on — computers located outside of Your state, province, country or other governmental jurisdiction where the data protection laws may differ than those from Your jurisdiction.
Your consent to this Privacy Policy followed by Your submission of such information represents Your agreement to that transfer.
The Company will take all steps reasonably necessary to ensure that Your data is treated securely and in accordance with this Privacy Policy and no transfer of Your Personal Data will take place to an organization or a country unless there are adequate controls in place including the security of Your data and other personal information.
Security of Your Personal Data
The security of Your Personal Data is important to Us, but remember that no method of transmission over the Internet, or method of electronic storage is 100% secure. While We strive to use commercially acceptable means to protect Your Personal Data, We cannot guarantee its absolute security
Analytics
We may use third-party Application providers to monitor and analyze the use of our Application.
Email Marketing
We may use Your Personal Data to contact You with newsletters, marketing or promotional materials and other information that may be of interest to You. You may opt-out of receiving any, or all, of these communications from Us by following the unsubscribe link or instructions provided in any email We send or by contacting Us.
Links to Other Websites
Our Application may contain links to other websites that are not operated by Us. If You click on a third party link, You will be directed to that third party's site or application. We strongly advise You to review the Privacy Policy of every site You visit.
We have no control over and assume no responsibility for the content, privacy policies or practices of any third party sites, services or applications.
Changes to this Privacy Policy
We may update Our Privacy Policy from time to time. We will notify You of any changes by posting the new Privacy Policy on this page.
We will let You know via email and/or a prominent notice on Our Application, prior to the change becoming effective and update the "Last updated" date at the top of this Privacy Policy.
You are advised to review this Privacy Policy periodically for any changes. Changes to this Privacy Policy are effective when they are posted on this page.
Contact Us
If you have any questions about this Privacy Policy, You can contact us: 
● By sending us an email: iago.nicolas@ufpe.br
